Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-19 paper/main.tex
Rough word count
rewrite method after having had a meeting with the boss

\begin{itemize}
    \item structure of last paragraph might be meh: methods/our approach
-> hypotheses -> results; readers might assume HARKing?
\end{itemize}

@@

\begin{itemize}
    \item Zwischenüberschriften rausnehmen, wenn Struktur so in Ordnung
    \item revise captions of Table 1 + 3 (regressors based on annotation of
    the other FG stimulus are now dropped from the table but mentioned in
    section "statistial model / contrasts")
\end{itemize}

@@

\begin{itemize}
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher der drei VIS Kontraste für welche VP genommen
    wurde
    \item location of tables \& figures is pretty confusing at the moment
    \item length of report of other reliably significant cluster across
        contrasts and report of control contrasts depends on if/how long they
        should be discussed
\end{itemize}

\noindent Discussion
\begin{itemize}
    \item umschreiben gemäß neuer Schwerpunktsetzung in Intro \& Method-Section
    \item \citep{bartels2004mapping, hasson2004intersubject}
    \item mehr zum Thema VIS( "best contrast was chosen")
\end{itemize}

@@

@@

@@

\subsubsection{Events}

\paragraph{movie}
% AV anno
For the analysis of the AV stimulus, we took advantage of a previously published
annotation of [the 869] movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment of the movie by either changing the perspective
within a setting or switching to another setting.
% AV regressors/events
Each cut was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale (e.g. room) that
was depicted for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

@@

    \caption{Overview of annotations and event counts in the whole audio-visual
    movie and individual stimulus segments.
    \texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
    \texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
    \texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and right
    half),
    \texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
    lower half),
    \texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
    \texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
    for every movie frame (\unit[40]{ms}).

@@

\paragraph{audio-description}

@@

    \caption{Overview of annotations and event counts in the whole
    audio-description and individual stimulus segments.

@@

\paragraph{Confounds for both}

\todo[inline]{Die Events für die low-level confounds habe erstmal hier
beschrieben; btw: Das Verschieben des Sounds in den Segmenten spiegelt sich
wahrscheinlich auch in den unterschiedlichen Counts der Events je Segment wider
(AV Bild vs AV Sound vs AO Sound)}

@@

\subsubsection{Hemodynamic Modeling}

@@

@@

% level 1 and 2; similarly to the reviewed studies that employed designed
% stimuli; we "based on stimulus annotations"
We then tested our modeled hemodynamic responses by conducting standard
two-level general linear model (GLM) analyses to create subject-specific results
($Z$-maps) across the 8 segments for every subject and each stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over subjects.

\paragraph{Design Matrix}

% AV design matrix
For the first level analysis of the AV stimulus, the modeled hemodynamic
responses related to all movie cuts (including \texttt{no\_cut}) and six
low-level perceptual confounds were included as regressors in the design matrix
(s. Table \ref{tab:av-events}).
% AD regressors in AV AD design matrix
For the first level analysis of the AD stimulus, the modeled hemodynamic
responses related to all noun categories and the two low-level perceptual
confounds were included (s. Table \ref{tab:ao-events}).
% AD regressors in AV
To create a contrasts of cross-modal control in the analysis of the AV stimulus,
we also implemented the regressors based on nouns used by the
audio-description's narrator to cue switches to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
To create contrasts of cross-modal negative control in the analysis of the AD
stimulus [and to capture variance of a possibly confounding change of the
soundscape after a cut], we implemented the movie cut-related regressors
(excluding \texttt{no\_cut}).
% both stimuli: null regressors
In analyses of both stimuli, a null regressor was chosen for a event category in
a segment, if that segment did not contain an event of the category (e.g. no
event of \texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

In this study, we investigated if increased hemodynamic activty in the PPA that
is usually defined by contrasting blocks of pictures can also be revealed by
contrasting selected stimulus features that we annotated in a audio-visual movie
and its audio-description.
% intro
To test the robustness of our approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
(2010) Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010);
but they did FFA}
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus e.g. objects or faces.
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

@@

\paragraph{GLM computations \& stuff}

% alignments single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
We co-registered the subjects in two ways.
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
On the one hand, subject-specific BOLD T2* time series were anatomically aligned
via linear transformation to a subject-specific, study-specific T2* template
(cf. \citep{sengupta2016extension}).
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
On the other hand, time series were aligned via non-linear transformation to a
study-specific T2* group template (cf. \citep{hanke2014audiomovie}).
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

@@

@@

@@

\todo[inline]{SE: Vergleich mit VIS kommt bestenfalls en passant; VIS selber
wird gar nicht berichtet, wäre aber wichtig zum Andocken an Literatur; COH: yes,
maybe reference Sengupta who are interested in the details? en passant makes
more sense here imo}

@@

\todo[inline]{individual results: AD trifft besser die VIS-PPA "trifft" als AV.
    Das ist zumindest sehr überraschend, oder?; COH: actually it isn't because
    of blindly averaging the actual frame content in the categories of movie
    cuts (cf. methods/regressors, discussion/shortcomings); this ``cross-modal
    control things'' seems to more confuse than having its merits}

@@

>>>>

\begin{itemize}
    \item make more concise if applicable
\end{itemize}

@@

\begin{itemize}
    \item -
\end{itemize}

@@

\begin{itemize}
    \item allgemein kürzen; insb. individual results kürzen
    \item consistencies across contrasts ausformulieren
    \item control contrasts ausformulieren
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
\end{itemize}

\noindent Discussion
\begin{itemize}
    \item umstrukturieren \& ggf. schon kürzen gemäß neuer Schwerpunktsetzung
    \item umschreiben gemäß neuer Schwerpunktsetzung
    \item mehr zum Thema VIS( "best contrast was chosen")
    \item \citep{bartels2004mapping, hasson2004intersubject}
\end{itemize}

@@

\todo[inline]{~1000 words}

@@

\todo[inline]{~3500 words}

@@

\subsubsection{Events related to high-level perception}

\todo[inline]{imo the subheadings for 2.6.1 and 2.6.2 can be dropped because
2.6.2 is super short}

% AV anno
For the analysis of the AV stimulus, we took advantage of a previously published
annotation of [the 869] movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment of the movie by either changing the perspective
within a setting or switching to another setting.
% AV regressors/events
Each cut was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}; e.g. a cut to the recurring waiting bench at the bus stop),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale (e.g. room) that
was depicted for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

@@

    \caption{Overview of annotated stimulus features of audio-visual
    movie.
    Respective event counts are given for the whole stimulus (\texttt{all} and
    the segments that were used for the eight sessions of fMRI scanning.
    %\texttt{fg\_av\_ger\_pd} (perceptual differences of consecutive frames),
    %\texttt{fg\_av\_ger\_ml} (mean luminance of a frame),
    %\texttt{fg\_av\_ger\_lr} (difference in mean luminance of left and right
    %half),
    %\texttt{fg\_av\_ger\_ud} (difference in mean luminance of upper and
    %lower half),
    %\texttt{fg\_av\_ger\_lrdiff} (left-right volume difference), and
    %\texttt{fg\_av\_ger\_rms} (root mean square volume) represent one event
    %for every movie frame (\unit[40]{ms}).

@@

@@

    \caption{Overview of annotated stimulus features of the audio-description.
    Respective event counts are given for the whole stimulus (\texttt{all} and
    the segments that were used for the eight sessions of fMRI scanning.

@@

\subsubsection{Events related to low-level perception / perceptual confounds}

\todo[inline]{das Verschieben des Sounds in den Segmenten spiegelt sich auch in
den unterschiedlichen Counts der Events je Segment wider (AV Bild vs AV Sound vs
AO Sound)}

@@

\subsection{Hemodynamic Modeling}

@@

% AV design matrix
For the subsequent first level GLM analysis, the modeled hemodynamic responses
related to all movie cuts (including \texttt{no\_cut}) and six low-level
perceptual confounds (s. Table \ref{tab:av-events}) were included as regressors
in the design matrix.
% AD regressors in AV AD design matrix
For the first level analysis of the AD stimulus, the modeled hemodynamic
responses related to all noun categories and the two low-level perceptual
confounds were included (s. Table \ref{tab:ao-events}).
% AD regressors in AV
To create a contrasts of cross-modal control in the analysis of the AV stimulus,
we also implemented the regressors based on nouns used by the
audio-description's narrator to cue switches to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
To create contrasts of cross-modal negative control in the analysis of the AD
stimulus [and to capture variance of a possibly confounding change of the
soundscape after a cut], we implemented the movie cut-related regressors
(excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was chosen for a event category in a segment,
if that segment did not contain an event of the category (e.g. no event of
\texttt{vpe\_old} in segment 3; cf. Table \ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

% level 1 and 2; similarly to the reviewed studies that employed designed
% stimuli; we "based on stimulus annotations"
We tested our modeled hemodynamic responses by conducting standard
two-level general linear model (GLM) analyses to create subject-specific results
($Z$-maps) across the 8 segments for every subject and each stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over subjects.

@@

% similar to previous studies
On the first level, we created GLM contrasts like studies that contrasted
blocks of pictures.
% dissimilar
But unlike previous studies, our approach was to contrast selected stimulus features that we annotated in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
(2010) Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010); but
they did FFA}
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
% AV: primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed that movie frames in these categories on average best represent
events that trigger perception of space versus e.g. objects or faces.
% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

@@

% alignments single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
Subject-specific BOLD T2* time series were anatomically co-registered in two
ways:
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
a) [time series were aligned to] via linear transformation to a
subject-specific, study-specific T2* template (cf.
\citep{sengupta2016extension}) and,
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
b) via non-linear transformation to a study-specific T2* group template (cf.
\citep{hanke2014audiomovie}).
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

\paragraph{2nd level}

@@

\paragraph{3rd level}

@@

\todo[inline]{~1300 words (some sections incomplete)}

@@

\todo[inline]{SE: VIS wird selbst gar nicht/en passant berichtet, wäre aber
wichtig zum Andocken an Literatur}

@@

\todo[inline]{individual results: AD trifft besser die VIS-PPA "trifft" als AV.
    Das ist zumindest sehr überraschend, oder?; COH: actually it isn't because
    of blindly averaging the actual frame content in the categories of movie
    cuts (cf. methods/regressors, discussion/shortcomings)}

@@

\todo[inline]{~2100 words (some sections incomplete)}
